%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%  REQUESTED MODULES/FUNDS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Requested modules/funds}
% Explain each item for each applicant (stating last name, first name).

\subsection{Basic Module}

\subsubsection{Funding for Staff}
\begin{funds}[funding for staff]
The following staff positions are requested for \fmhkn{xx} years each:

\positionmul{Research associate, TV-L 13, 36 months}{5750}{36}
\positionmul{1/2 WHB, 36 months}{545}{36}

\end{funds}


\subsubsection{Direct Project Costs}
\begin{funds}[direct project costs]

\subsubsubsection{Equipment up to 10\,000\,\euro, Software and Consumables}

% \position{Some device}{3000}

None. 

\subsubsubsection{Travel Expenses}

We apply for an international and a European conference trip (IEEE,
ACM, or similar), each year. Per trip, we estimate conference fees of
about 1000 €. For international conferences, we calculate 1500 €
travel cost; for European conferences, 750 €. This results in a total
of 4250 € per year. 


\position{Travel}{12750}

\subsubsubsection{Visiting Researchers \textnormal{(excluding Mercator Fellows)}}
None. (See below for the proposed Mercator Fellows.) 

\subsubsubsection{Expenses for Laboratory Animals}
None.

\subsubsubsection{Other Costs}
None.

\subsubsubsection{Project-related publication expenses}
% We apply for a total of 1500\euro\ for publication expenses (750\,\euro\ per
% year). Furthermore, we will submit articles to open access preprint repositories
% such as \href{https://www.biorxiv.org/}{\textit{bioRxiv}}.

Publication cost will be covered by conferences fees (see above). We
will not publish in journals that extort payment for publication but
will use journals with an acceptable Open Access policy. 

% \position{Publication costs}{1500}

\end{funds}

\subsubsection{Instrumentation}

\subsubsubsection{Equipment exceeding 10\,000\,\euro}

No additional equipment is required. 

\subsubsubsection{Major Instrumentation exceeding 50\,000\,\euro}

No additional major instrumentation is required. 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The following are additional/other modules one might want to apply for
%% otherwise, just delete/comment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \vspace*{2cm}\fmhkn{The following are additional/other modules one might want to apply for. Otherwise, just delete/comment}

\subsection{Module Temporary Position for Principal Investigator}

Not required. 

\subsection{Module Replacement Funding}

Not required. 

\subsection{Module Temporary Clinician Substitute}

Not required. 


\subsection{Module Mercator Fellows}
\fmhkn{Text}

\subsection{Module Workshop Funding}

Not required. 


\subsection{Module Public Relations Funding}

Not required. 


